### 2012-11-25 paper.tex
Changed some tables

\begin{table}[h]
\centering
\begin{tabular}{|llllllll|}
	\hline
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  &Class\\
	\hline
									&0         	&0         &0         	&0       &  0         & 0.5      &0\\
  								&1         	&1         &0.959     	&1       &0.979       &	0.5      &1\\
  \hline
	Weighted Avg.		&0.959     	&0.959     &0.919   		&0.959   &0.939     	&0.5	&\\
	\hline
\end{tabular}
\caption{Results of the SVM-classification for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|llllllll|}
	\hline
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &ROC Area  &Class\\
	\hline
									&0         	&0         &0         &0       &  0         & 0.5      &0\\
  								&1         	&1         &0.959     &1       &0.979       &	0.5      &1\\
  \hline
	Weighted Avg.		&0.959     	&0.959     &0.919   	&0.959   &0.939     	&0.5				&\\
	\hline
\end{tabular}
\caption{Results of the kNN-classification for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|llllllll|}
	\hline
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure &ROC Area  	&Class\\
	\hline
									&0.568     	&0.062     &0.744     	&0.568   &0.644    	&0.753    	&	>50K\\
  								&0.938     	&0.432     &0.873     	&0.938   &0.904     &0.753    	&$\leq$50K\\
  \hline
	Weighted Avg.   & 0.849    & 0.343     &0.842   		&0.849   &0.842     & 0.753			&\\
	\hline
\end{tabular}
\caption{Results of the SVM-classification for the adult dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|llllllll|}
	\hline
									&TP Rate   &FP Rate   &Precision   &Recall  &F-Measure &ROC Area  	&Class\\
	\hline
									&0.593     &0.088      &0.68      &0.593     &0.633    &0.884    		&>50K\\
									&0.912     &0.407      &0.876     &0.912     &0.893    &0.884    		&$\leq$50K\\
  \hline
	Weighted Avg.   &0.835     &0.331      &0.829     &0.835     &0.831    &0.884 \\
	\hline
\end{tabular}
\caption{Results of the kNN-classification for the adult dataset}
\end{table}

@@

\subsection{Desicion Tree}

@@

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class \\   \midrule
               &  0.52    & 0.223   & 0.635     & 0.52   & 0.572     & 1  \\   \midrule
               &  0.526   & 0.245   & 0.385     & 0.526  & 0.445     & 2  \\
               &  0.481   & 0.268   & 0.488     & 0.481  & 0.485     & 3  \\
Weighted Avg.  &  0.508   & 0.243   & 0.528     & 0.508  & 0.513     &    \\   \bottomrule
    \end{tabular*}
\caption{Naive Bayes} 
\label{tab:contra:bayes:1d}
\end{table*}

@@

\subsection{Support VectorMachine}

@@

\begin{table}[h]
\centering
\begin{tabular}{|llllllll|}
	\hline
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  	&Class\\
	\hline
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		&0.628    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	&0.648    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	&0.614    	&3\\
  \hline
	Weighted Avg.   & 0.849    & 0.343      &0.842   &  0.849     &0.842     & 0.753			&\\
	\hline
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|llllllll|}
	\hline
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  	&Class\\
	\hline
									&0.569     	&0.351     &0.547     	&0.569   &0.558      	&0.65     	&1\\
                 	&0.414     	&0.166     &0.422     	&0.414   &0.418      	&0.677    	&2\\
                 	&0.438     	&0.279     &0.455     	&0.438   &0.447      	&0.603    	&3\\
  \hline
	Weighted Avg.   &0.489     	&0.284     &0.487     	&0.489   &0.488      	&0.64			&\\
	\hline
\end{tabular}
\caption{Results of the kNN-classification for the contraception dataset}
\end{table}

>>>>

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  &Class\\
	\midrule
									&0         	&0         &0         	&0       &  0         & 0.5      &0\\
  								&1         	&1         &0.959     	&1       &0.979       &	0.5      &1\\

	Weighted Avg.		&0.959     	&0.959     &0.919   		&0.959   &0.939     	&0.5	&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &ROC Area  &Class\\
	\midrule
									&0         	&0         &0         &0       &  0         & 0.5      &0\\
  								&1         	&1         &0.959     &1       &0.979       &	0.5      &1\\

	Weighted Avg.		&0.959     	&0.959     &0.919   	&0.959   &0.939     	&0.5				&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure &ROC Area  	&Class\\
	\midrule
									&0.568     	&0.062     &0.744     	&0.568   &0.644    	&0.753    	&	>50K\\
  								&0.938     	&0.432     &0.873     	&0.938   &0.904     &0.753    	&$\leq$50K\\

	Weighted Avg.   & 0.849    & 0.343     &0.842   		&0.849   &0.842     & 0.753			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the adult dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   &FP Rate   &Precision   &Recall  &F-Measure &ROC Area  	&Class\\
	\midrule
									&0.593     &0.088      &0.68      &0.593     &0.633    &0.884    		&>50K\\
									&0.912     &0.407      &0.876     &0.912     &0.893    &0.884    		&$\leq$50K\\

	Weighted Avg.   &0.835     &0.331      &0.829     &0.835     &0.831    &0.884 \\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the adult dataset}
\end{table}

@@

@@

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class \\   \midrule
               &  0.52    & 0.223   & 0.635     & 0.52   & 0.572     & 1  \\  
               &  0.526   & 0.245   & 0.385     & 0.526  & 0.445     & 2  \\
               &  0.481   & 0.268   & 0.488     & 0.481  & 0.485     & 3  \\
Weighted Avg.  &  0.508   & 0.243   & 0.528     & 0.508  & 0.513     &    \\   \bottomrule
    \end{tabular*}
\caption{Naive Bayes} 
\label{tab:contra:bayes:1d}
\end{table*}

@@

@@

\begin{table}[htb]
\centering
\begin{tabular}{llllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  	&Class\\ 
	\midrule
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		&0.628    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	&0.648    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	&0.614    	&3\\
	Weighted Avg.   & 0.849    & 0.343      &0.842   &  0.849     &0.842     & 0.753			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  	&Class\\
	\midrule
									&0.569     	&0.351     &0.547     	&0.569   &0.558      	&0.65     	&1\\
                 	&0.414     	&0.166     &0.422     	&0.414   &0.418      	&0.677    	&2\\
                 	&0.438     	&0.279     &0.455     	&0.438   &0.447      	&0.603    	&3\\

	Weighted Avg.   &0.489     	&0.284     &0.487     	&0.489   &0.488      	&0.64			&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the contraception dataset}
\end{table}
